---
title: "Climatology Plot of Panjshir catchment"
author: "kabiraj"
date: "12/28/2020"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=TRUE)
```

## Background 

This document shows the code for generating the climatology plot of the Panjshir catchment. The temperature and precipitation are extracted from the base model having the input of the ERA data and the monthly average temperate and precipitation are plotted. Firstly, old files are removed and required library are imported

```{r, message=FALSE}
  rm(list =ls())

  library(data.table)
  library(dplyr)
  library(ggplot2)

```

Next, the data is imported 
```{r}
indir <- "E:\\Panjshir_snowcover_paper_Santosh\\input_files_4figure\\baseERAmodel_input\\"
outdir <- "E:\\Panjshir_snowcover_paper_Santosh\\outputFIGURES\\"

```

## Data waggling  
### Preparation for the precipitation data
```{r,  warning=FALSE}
#read data
rain <- fread(paste(indir,"rain.dat",sep=""),skip = 16)
#head(rain)
rain$DailyPavg = rowMeans(rain[,-1], na.rm = TRUE)

#look at the format of the computer date and change accordingly if required 
rain$Date <- as.Date(rain$V1, format= "%Y-%m-%d")
rain$Year <- format(as.Date(rain$Date), format= "%Y")
rain$Month <- format(as.Date(rain$Date), format= "%m")

#selecting only the average value from the data 
rain2 <- rain %>%
  select(Date, Year, Month, DailyPavg)

#quick view of the data 
head(rain2)

```
### preparation of the temperature data
```{r,  warning=FALSE}
#read data
tavg <- fread(paste(indir,"tmean.dat",sep=""),skip = 16)

#finding the ncol(tavg) and selecting the data 
tavg$DailyTavg <- rowMeans(tavg[, 2:53], na.rm = TRUE)

tavg$Date <- as.Date(tavg$V1, format= "%Y-%m-%d")

#selecting only the daily average temperature of each date
 tavg2 <- tavg %>%
   select(Date, DailyTavg)

#Quick outlook of the first five rows of the data
head(tavg2)

```

Now merging two table and fixing the study duration 
```{r,  message=FALSE}
#merging both the Precipitation and temperature data together
PT <- merge(x = rain2, y = tavg2, by = "Date", all = TRUE)

#keeping only the required column
PT2 <- PT %>%
  select(Date, Year, Month, DailyPavg, DailyTavg )

#Calculation for each month for analysis
yearNmonth <- PT2 %>% 
                group_by(Year,Month) %>% 
                filter(Year <= 2010) %>%
                filter(Year >= 1981) %>%
                summarise(Precip = round(sum(DailyPavg),0),
                          AvgTemp = round(mean(DailyTavg),0))
    
#Monthly Calculation 
Annualprecip <- yearNmonth %>%
                group_by(Month) %>%
                summarise(AP = round(mean(Precip),0),
                          AT = round(mean(AvgTemp),0))

```


## Visulization
Our aim is to keep both the temperature and precipitaiton in a single plot, however initially the individual plots are plotted before making final plot. 

### Monthly average precipitaiton plot 
```{r}
ggplot(data = Annualprecip) +
  geom_bar(mapping = aes(x = Month, y = AP), stat = "identity") + 
  ylab("Precipitation (mm)")
```

### Monthly average temperature plot
```{r}
ggplot(data = Annualprecip) +
  geom_point(mapping = aes(x = Month, y = AT)) + 
  geom_line(mapping = aes(x = Month, y = AT, group = 1)) + 
  ylab(expression("Temperature ("~degree~"C)"))

```

### Climatology plot of the region 

```{r}
#defining the minimimun of the variables
ylim.prim <- c(0, 120) #for precip
ylim.sec <- c(-20, 10) #for temp
b <- diff(ylim.prim)/diff(ylim.sec)
a <- b*(ylim.prim[1] - ylim.sec[1])

#plot
ggplot(data = Annualprecip) +
  geom_bar(mapping = aes(x = Month, y = AP), stat = "identity", fill="blue", alpha= 0.5) + 
  geom_point(mapping = aes(x = Month, y = a+AT*b), color= "red", size = 2.5) + 
  geom_line(mapping = aes(x = Month, y = a+AT*b, group = 1), color = "red", size =1.5) + 
  scale_y_continuous("Precipitation (mm)", 
                     sec.axis = sec_axis(~ (. - a)/b, 
                                         name = expression("Temperature ("~degree~"C)"))) +
  theme_bw() + 
  theme(axis.title=element_text(size=30),axis.text = element_text(size=25),
      axis.text.x = element_text(angle = 90, vjust = .5),
      strip.text = element_text(size = rel(3),colour = "black"),
      legend.key.width = unit(1, "cm"), legend.key.height = unit(1.2, "cm"),
      legend.text = element_text(size = rel(2)),legend.title = element_text(size = rel(2.5))) +
  theme(axis.line.y.right = element_line(color = "red"),
        axis.ticks.y.right = element_line(color = "red"),
        axis.text.y.right = element_text(color = "red"),
        axis.title.y.right = element_text(color = "black")
        ) +
  #  ggtitle("Climatology for Panjshir (1981-2010)") +
  scale_x_discrete(labels=month.abb)  


```

Output is saved in the following location 
```{r}
ggsave("E:\\Panjshir_snowcover_paper_Santosh\\outputFIGURES\\PanjshirClimatology1.png", width = 7.5, height = 6, units = "in")

```

### Hence the climatology of the region is prepared. 




