---
title: "Hypsometry of Panjshir catchment"
author: "kabiraj"
date: "12/28/2020"
output: html_document
---

<!-- # ```{r setup, include=FALSE} -->
<!-- # knitr::opts_chunk$set(echo = TRUE) -->
<!-- # ``` -->

## Background

Hypsometry describes the distribution of elevation of land with respect to occupied area. A hypsometric curve is a histogram or cumulative distribution function of elevations in a geographical area.

Firstly the library and data are imported 

```{r, message=FALSE}
  rm(list =ls())

  library(data.table)
  library(dplyr)
  library(ggplot2)

```

## Data waggling 

Next, the data is imported 
```{r}
indir <- "E:/Panjshir_snowcover_paper_Santosh/input_files_4figure/baseERAmodel_input/"
outdir <- "E:/Panjshir_snowcover_paper_Santosh/outputFIGURES/"

#read header names
variable_head <- unlist(strsplit(scan(paste(indir,"hrus.par",sep=""),"",nlines = 1,skip = 1,sep = "\n"),split = "\t"))

#read data
hrus <- fread(paste(indir,"hrus.par",sep=""),skip = 5)

#assign column names
colnames(hrus) <- variable_head

#removing the last row
hrus1 <- head(hrus,-1)

#Selecting the area and elevation from the data frame
AreaElevation <- hrus1 %>%
  transmute(Area = area,
            Elevation = elevation)

#defining the elevation range
Erange <- c(1000, 1500, 2000, 2500, 3000, 3500, 4000, 4500, 5000, 5500, 6000)

#creating an empty matrix
emptyTable <- matrix(data=NA, nrow = length(Erange), ncol = 3)

#Keeping the range of elevation in the thrid column
emptyTable[,3] <- Erange

#sum of the elevation below that range 
for(i in 1:length(Erange)) {
one <-  filter(AreaElevation, Elevation < Erange[i] )
emptyTable[i, 1] <- sum(one$Area)
}

#making sure it as data frame
emptyTable2 <- as.data.frame(emptyTable) 

#converting the area into the km2
emptyTable2$V2 <- round(emptyTable2$V1 /1000000, 0)


```

## Visulization


```{r}
ggplot(data = emptyTable2) +
  geom_line(mapping = aes(x = V3, y = V2), color = "blue", size =1.5) +
  geom_point(mapping = aes(x = V3, y = V2), color = "blue", size =2) +
  ylab("Cumulative area (km2)") + xlab("Elevation (%)") + 
  geom_segment( aes(x = V3, xend=V3, y=0, yend=V2), color = "black") +
  theme_bw() + 
  theme(axis.title=element_text(size=30),axis.text = element_text(size=25),
        axis.text.x = element_text(angle = 0, vjust = .5),
        strip.text = element_text(size = rel(3),colour = "black"),
        legend.key.width = unit(1, "cm"), legend.key.height = unit(1.2, "cm"),
        legend.text = element_text(size = rel(2)),legend.title = element_text(size = rel(2.5)))

```


Output is saved in the following location 
```{r}
ggsave("E:\\Panjshir_snowcover_paper_Santosh\\outputFIGURES\\1PanjshirHypsometry1.png", width=200,height=140,units="mm",dpi = 600, scale = 1)

```

### Hence the Hypsometry of the region is prepared. 

```{r,  include=FALSE}
#keeping it just as an alternative
ggplot(data = emptyTable2) +
  geom_line(mapping = aes(x = V3, y = V2), color = "blue", size =1.5) +
  geom_point(mapping = aes(x = V3, y = V2), color = "blue", size =2) +
  ylab("Cumulative area (km2)") + xlab("Elevation (%)") + 
  geom_segment( aes(x = 0, xend=V3, y=V2, yend=V2), color = "black") +
  theme_bw() + 
  theme(axis.title=element_text(size=30),axis.text = element_text(size=25),
        axis.text.x = element_text(angle = 0, vjust = .5),
        strip.text = element_text(size = rel(3),colour = "black"),
        legend.key.width = unit(1, "cm"), legend.key.height = unit(1.2, "cm"),
        legend.text = element_text(size = rel(2)),legend.title = element_text(size = rel(2.5)))
        
```

