---
title: "snowDaily"
author: "kabiraj"
date: "12/29/2020"
output: html_document
---

<!-- # ```{r setup, include=FALSE} -->
<!-- # knitr::opts_chunk$set(echo = TRUE) -->
<!-- # ``` -->

## Background

Hypsometry describes the distribution of elevation of land with respect to occupied area. A hypsometric curve is a histogram or cumulative distribution function of elevations in a geographical area.

Firstly the library and data are imported 

```{r, message=FALSE}
rm(list=ls())

library(data.table)
library(dplyr)
library(ggplot2)
library(zoo)
library(scales)
library(ggpubr) #used in the pearson coefficient

```

## Data waggling 

Next, the data is imported 
```{r}
indir <- "E:/Panjshir_snowcover_paper_Santosh/input_files_4figure/baseERAmodel_input/"
outdir <- "E:/Panjshir_snowcover_paper_Santosh/outputFIGURES/"

#read header
header <- unlist(strsplit(scan(paste(indir,"TimeLoop_1981-2018.dat",sep=""),"",nlines = 1,skip = 5,sep = "\n"),split = "\t"))
#get the timeloop
timeloop <- fread(paste(indir,"TimeLoop_1981-2018.dat",sep=""),skip = 10) 

#keep the length of the timeloop same as header length 
timeloop <- timeloop[,1:length(header)]
#keep the header names 
colnames(timeloop) <- c(header)

#extract the month and years 
timeloop$Dates <- as.Date(timeloop$ID, "%Y-%m-%d")
timeloop$Year <- format(timeloop$Dates,"%Y")
timeloop$Month <- format(timeloop$Dates,"%m")
#timeloop$Day <- format(timeloop$Dates,"%d")

timeloop$modisSnow[timeloop$modisSnow=="Inf"]<-NA

# for the timeseries and scatter plot
analysis1 <-	timeloop %>%
                filter(Year <= 2018) %>%
                filter(Year >= 2003) %>%
                mutate(MODISMovingMean = (rollmean(modisSnow, 8, fill = NA, partial=TRUE)),
                       J2KMovingMean = (rollmean(snowCoverAreaT, 8, fill = NA,  partial=TRUE))) #/1000000))		

#for monthly bar graph 	
analysis2 <- analysis1 %>%	
             group_by(Month) %>%
             summarize (MODIS =mean(MODISMovingMean, na.rm=TRUE),
                        Model = mean(J2KMovingMean, na.rm=TRUE))		

AnnualPlot <- reshape2::melt(analysis2, id.vars='Month')


#for daily min-max graph 	
analysis3 <- analysis1 %>%	
             group_by(Year) %>%
             transmute(ModelDaily = snowCoverAreaT,
                        dAYS = sequence(n()))

analysis4 <- analysis3 %>%
             group_by(dAYS) %>%
             mutate(MeanDay = mean(ModelDaily, na.rm = TRUE))
#since it is mean of the day wise we can remove the other values
analysis4$MeanDay[366:5844] <- NA


```

##Visulizaation
```{r, warning= FALSE}

ggplot(analysis1, aes(Dates)) +
  geom_point(aes(y=MODISMovingMean, colour="MODIS (8 days)"), size = 0.65, shape= 1)+
  geom_point(aes(y=J2KMovingMean, colour="Model (8 days)"), size = 0.65, shape = 2) +
  geom_line(aes(y=snowCoverAreaT, colour="Model (Daily)"))+
  #scale_x_continuous(name = "Year", limits = c(2003,2018), breaks = seq(2003,2018, 2)) + #to find the range of data to be displayed will fix latter
  labs(x="Year",
       y=expression(Snow~Cover~Area~(km^{2}))) +
  theme_bw() + 
  scale_colour_manual(" ",
                   breaks = c("MODIS (8 days)", "Model (8 days)", "Model (Daily)"), 
                   values=c("blue", "red", "black")) +
  theme(axis.title=element_text(size=23),axis.text = element_text(size=18)) +
  theme(legend.direction = "horizontal", legend.position = "bottom", legend.text=element_text(size=15)) +
  guides(shape= FALSE) 
##keeping this guide at the end to remove the line in he points but not successful :)

```

saving the data 
```{r}

ggsave("E:\\Panjshir_snowcover_paper_Santosh\\outputFIGURES\\2a_dailySnowCocverarea.png", width = 7.5, height = 4, units = "in")


```

### Scatter plot between the modis and model snow cover area 

```{r, warning= FALSE}

ggplot(analysis1, aes(x=MODISMovingMean, y=snowCoverAreaT)) + 
#ggplot(analysis1, aes(x=modisSnow, y=snowCoverAreaT)) + 
#ggplot(analysis1, aes(x=MODISMovingMean, y=J2KMovingMean)) +  
  geom_point(color="red", alpha= 0.37) + 
  geom_smooth(method=lm, se=FALSE) +
  labs(x=expression(Modis~Area~(km^{2})),
       y=expression(MODEL~Area~(km^{2}))) +
  theme_bw() +
  stat_cor(method = "pearson", label.x = 50, label.y = 2050) +
  theme(axis.title=element_text(size=23),axis.text = element_text(size=18))

```


```{r}

ggsave("E:\\Panjshir_snowcover_paper_Santosh\\outputFIGURES\\2b_ScatterdailySnowCocverarea.png", width = 6.5, height = 6.5, units = "in")


```



```{r}

ggplot(data = AnnualPlot, aes(x = Month, y = value, fill = variable, group = variable)) + 
  geom_col(position='dodge', alpha= 0.56)+ ##stat='identity',
  labs(x="Months",
     y=expression(Area~(km^{2}))) +
  scale_y_continuous(labels = comma) +
  theme_bw() +
  scale_x_discrete(labels=month.abb) +
  scale_fill_manual("", values = c("MODIS" = "blue", "Model" = "red")) +
   theme(axis.title=element_text(size=25),axis.text = element_text(size=17)) +
   theme(legend.direction = "horizontal", 
         legend.position = "bottom", 
         legend.title = element_blank(), 
         legend.text=element_text(size=16)) 

```



```{r}

ggsave("E:\\Panjshir_snowcover_paper_Santosh\\outputFIGURES\\2c_MonthlySnowCocverarea.png", width = 7.5, height = 5.8, units = "in")


```

#for daily scatter

```{r}

ggplot(analysis4) + 
  geom_line(aes(x=dAYS, y = ModelDaily, color="Range of snow cover"), alpha= 0.27) +
  geom_point((aes(x= dAYS, y= MeanDay, color = "Average of days snow cover"))) +
    theme_bw() + 
  scale_colour_manual(" ",
                   breaks = c("Range of snow cover", "Average of days snow cover"), 
                   values=c("gray44", "red")) +
  labs(x="Days",
     y=expression(Area~(km^{2}))) +
  scale_y_continuous(labels = comma) +
  theme(axis.title=element_text(size=25),axis.text = element_text(size=17)) +
  theme(legend.direction = "horizontal", 
         legend.position = "bottom", 
         legend.title = element_blank(), 
         legend.text=element_text(size=16)) 




```

```{r}

ggsave("E:\\Panjshir_snowcover_paper_Santosh\\outputFIGURES\\2d_DailyScatterSnowCocver.png", width = 7.5, height = 5.8, units = "in")


```

