---
title: "SoilWaterEquivalent"
author: "kabiraj"
date: "12/30/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Background

Hypsometry describes the distribution of elevation of land with respect to occupied area. A hypsometric curve is a histogram or cumulative distribution function of elevations in a geographical area.

Firstly the library and data are imported 

```{r, message=FALSE}
#removing the old files
rm(list =ls())

#required package 
library(data.table)
library(dplyr)
library(ggplot2)
library(reshape2)

```

## Data waggling 

Next, the data is imported 
```{r}
indir <- "E:/Panjshir_snowcover_paper_Santosh/input_files_4figure/baseERAmodel_input/"
outdir <- "E:/Panjshir_snowcover_paper_Santosh/outputFIGURES/"

#read header
header <- unlist(strsplit(scan(paste(indir,"TimeLoop_1981-2018.dat",sep=""),"",nlines = 1,skip = 5,sep = "\n"),split = "\t"))
#get the timeloop
timeloop <- fread(paste(indir,"TimeLoop_1981-2018.dat",sep=""),skip = 10) 

#keep the length of the timeloop same as header length 
timeloop <- timeloop[,1:length(header)]
#keep the header names 
colnames(timeloop) <- c(header)

#extract the month and years 
timeloop$Dates <- as.Date(timeloop$ID, "%Y-%m-%d")
timeloop$Year <- format(timeloop$Dates,"%Y")
timeloop$Month <- format(timeloop$Dates,"%m")

#Monthly Calculation for each year for analysis
MonthlyValue1 <- timeloop %>% 
                group_by(Month) %>% 
                summarise(AvgSWE = round(mean(snowTotSWE),0),
                           AvgSmelt = round(mean(snowMelt),0),
                          AvgSolRad = round(mean(solRad),0),
                          AvgTmax = round(mean(tmax),0))

#converting to data frame
MonthlyValue <- as.data.frame(MonthlyValue1)

#creating the scale factor for the range of y axis 
scaleFactor <- max(MonthlyValue$AvgSWE) / max(MonthlyValue$AvgSmelt)

```


## Visulization
```{r}

#plotting 
ggplot(MonthlyValue, aes(x=Month,  width=.4)) +
  geom_col(aes(y=AvgSWE), fill="blue", position = position_nudge(x = -.4), alpha =0.4) +
  geom_col(aes(y=AvgSmelt * scaleFactor), fill="red", alpha = 0.4) +
  scale_y_continuous(name="Snow Water Equivalent (mm/day)", 
                     sec.axis=sec_axis(~./scaleFactor, name="Snowmelt (mm/day)")) +
  theme_bw() +
  theme(
    axis.title.y.left=element_text(color="blue"),
    axis.text.y.left=element_text(color="blue"),
    axis.title.y.right=element_text(color="red"),
    axis.text.y.right=element_text(color="red"),
    axis.line.y.left = element_line(color = "blue"),
    axis.line.y.right = element_line(color = "red")) +
  labs(title = "Snow water equivalent and snow melt", x = "Months") +
  theme(axis.title=element_text(size=20),axis.text = element_text(size=16),
        axis.text.x = element_text(angle = 0, vjust = .5)) +
  scale_x_discrete(labels=month.abb)
```




saving the data 
```{r}

ggsave("E:\\Panjshir_snowcover_paper_Santosh\\outputFIGURES\\5b_SWEvsSmelt.png", width = 7, height = 6, units = "in")


```


##snowWaaterEquivalent vs snowmelt plot 

```{r}
scaleFactor2 <- max(MonthlyValue$AvgSolRad) / max(MonthlyValue$AvgTmax)

ggplot(MonthlyValue, aes(x=Month,  width=.4)) +
  geom_col(aes(y=AvgSolRad), fill="blue", position = position_nudge(x = -.4), alpha =0.4) +
  geom_col(aes(y=AvgTmax * scaleFactor2), fill="red", alpha = 0.4) +
  scale_y_continuous(name="Solar Radiation (W/m2)", 
                     sec.axis=sec_axis(~./scaleFactor2, name="Maximum Temperature (*C)")) +
  theme_bw() +
  theme(
    axis.title.y.left=element_text(color="blue"),
    axis.text.y.left=element_text(color="blue"),
    axis.title.y.right=element_text(color="red"),
    axis.text.y.right=element_text(color="red"),
    axis.line.y.left = element_line(color = "blue"),
    axis.line.y.right = element_line(color = "red")) +
  labs(title = "Solar radiation and Maximum Temperature", x = "Months") +
  theme(axis.title=element_text(size=20),axis.text = element_text(size=16),
        axis.text.x = element_text(angle = 0, vjust = .5),
        strip.text = element_text(size = rel(3),colour = "black"),
        legend.key.width = unit(1, "cm"), legend.key.height = unit(1.2, "cm"),
        legend.text = element_text(size = rel(2)),legend.title = element_text(size = rel(2.5))) +
  scale_x_discrete(labels=month.abb)
```

```{r}



ggsave("E:\\Panjshir_snowcover_paper_Santosh\\outputFIGURES\\5a_SWEvsSmelt.png", width = 7.6, height = 6, units = "in")


```
